\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-25 trunk/europa-basics.tex
updates to review

\begin{figure}[b]
\centering
  \includegraphics[scale=0.35]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints on the
variables: $C=\{c_1(x_1,..,x_N), ..., c_K(x_1,..,x_N)\}$, the
objective is to find one or more value assignments to $V$ where all
constraints are satisfied. To solve a problem, \textsf{CP} techniques
use logical inference to perform Constraint Propagation, which
consists of two operations:

>>>>

\begin{figure}[b]
\centering
  \includegraphics[scale=0.45]{figs/shopping_europa.pdf}
  \caption{\small A potential plan for a robot shopping for groceries.}
\label{fig:shop:shopping}
\end{figure}

@@

A constraint programming problem consists of a set of variables $V=
{x_1,..,x_N}$, where each variable takes values from a domain
$d_1,..,d_N$; in this chapter we will deal only with discrete and
finite domains. Given a defined conjunctive set of constraints
\kcomment{\cite{gen87}} on the variables: $C=\{c_1(x_1,..,x_N), ...,
c_K(x_1,..,x_N)\}$, the objective is to find one or more value
assignments to $V$ where all constraints are satisfied. To solve a
problem, \textsf{CP} techniques use logical inference to perform
Constraint Propagation, which consists of two operations:

### 2012-04-25 trunk/related.tex
updates to review

\begin{figure}[htpb]
 \centering
 \includegraphics[scale=0.3]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an AI based
   Planner.}
 \label{fig:planner}
\end{figure}

@@

Planning and plan execution are not new to the overall field of
robotics. Early motivation of building computational mechanisms for
decision making were intended to be deployed on robotic devices by
very definition. The seminal volume \cite{computersthought} very
clearly articulates how physical manifestation of robots could be
controlled by task planning and execution. The very first planner
\cite{green69} was an exercise in computational theorem proving with
early state space planners popularized by \texttt{STRIPS}
\cite{strips71} dominating the academic landscape. An early
demonstration of planning as a situated agent was the highly
influential \texttt{Shakey} the robot experiment
\cite{shakey84}. Subsequent work driven largely by defense funding in
the United States sequestered the discipline in academic labs
principally applied for algorithmic development and if embedded then
in testing within the confines of modest indoor settings. The leap to
applying them for real world problem solving is relatively new and
driven largely by NASA applications pioneered by \cite{mus94,mus98,
  jonsson00, rajan00, chien05, bresina05}.

@@

It was with the demonstration of \texttt{RAX} $65$ Million miles in
outer space, that temporal reasoning using methods came to the
forefront of AI planning and for situated agents. Lessons learned from
\texttt{RAX} led to the development of \texttt{IDEA}
\cite{mus02,mus04,Dias:2003ua,mus06} with the central theme of using
planners collectively for problem solving arose. Another critical
theme was iteratively and incremental plan repair of an anytime plan
\cite{Zaimag96} as proposed by \texttt{CASPER} \cite{chien00}.

>>>>

\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.4]{figs/planner-arch.pdf}
 \caption{\small A general architectural block diagram for an AI based
   Planner.}
 \label{fig:planner}
\end{figure}

@@

Planning and plan execution are not new to the overall field of
robotics. Early motivation of building computational mechanisms for
decision making were intended to be deployed on robotic devices by
very definition. The seminal volume \cite{computersthought} very
clearly articulates how physical manifestation of robots could be
controlled by task planning and execution. The very first planner
\cite{green69} was an exercise in computational theorem proving with
early state space planners popularized by \texttt{STRIPS}
\cite{strips71} dominating the academic landscape. An early
demonstration of planning as a situated agent\footnote{\kcomment{By
    \emph{situated} we emphasize that an agent is embedded within a
    physical robot.}} was the highly influential \texttt{Shakey} the
robot experiment \cite{shakey84}. Subsequent work driven largely by
defense funding in the United States sequestered the discipline in
academic labs principally applied for algorithmic development and if
embedded then in testing within the confines of modest indoor
settings. The leap to applying them for real world problem solving is
relatively new and driven largely by NASA applications pioneered by
\cite{mus94,mus98, jonsson00, rajan00, chien05, bresina05}.

@@

It was with the demonstration of \texttt{RAX} $65$ Million miles in
outer space, that temporal reasoning using \kcomment{planning} methods
came to the forefront of AI Planning for situated agents. Lessons
learned from \texttt{RAX} led to the development of \texttt{IDEA}
\cite{mus02,mus04,Dias:2003ua,mus06} with the central theme of using
planners collectively for problem solving arose. Another critical
theme was iteratively and incremental plan repair of an anytime plan
\cite{Zaimag96} as proposed by \texttt{CASPER} \cite{chien00}.
